Signal Processing to Demodulate FM Radio

### 2020-12-11 doc/paper/paper.tex
wip

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Signal Processing for Broadcast FM Radio Demodulation}

@@

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Signal Processing to Demodulate FM Radio}

@@

  This paper describes the necessary parts of signal processing, in order to listen to a radio station that is broadcast in the FM frequency band. Frequency modulation (FM) is a widely used standard to provide [...]
